Measuring neutron star tidal deformability with Advanced LIGO: a Bayesian analysis of mixed binary observations

### 2016-05-24 Paper/paper.tex
text abt cbcs

\red{
Text about CBCs. How was each type observed so far?
}
\prayush{
Coalescing binaries of compact objects, i.e. black holes (BH) and/or
neutron stars (NS) are the primary target sources for 
aLIGO~\cite{Abbott:2016nhf,LIGOVirgo2016a}.
% 
Compact binary merger rate estimates suggest
a GW detection rate of approximately a few tens of binary black holes
(BBH) every year~\cite{Abadie:2010cfa}. The actual masses of
astrophysical black holes are uncertain, but observations and
population synthesis studies suggest that BHs formed from stellar
core-collapse can have masses up to and higher than
$34M_\odot$~\cite{2008ApJ...678L..17S,2010ApJ...714.1217B}.  Also,
recent measurements using continuum fitting and X-ray reflection
fitting suggest that black holes can have high spin, with the BH
angular momentum in dimensionless units exceeding
$0.8$~\cite{2011ApJ...742...85G,2012MNRAS.424..217F,Gou:2013dna,
  2009ApJ...697..900M,McClintock:2006xd,Miller:2009cw,McClintock:2013vwa}.
Therefore the observations of GWs emitted by spinning BBHs will allow us to
understand the spin-spin and spin-orbit dynamics of the two-body
system, apart from allowing us to test strong-field dynamics of
General Relativity.
}
%

>>>>

\red{
Text about CBCs. How was each type observed so far?
}
Coalescing compact binaries (both monolithic and mixed) of stellar-mass black
holes (BH) and neutron stars (NS) are the primary target sources for the second
generation GW detectors~\cite{Timmes:1995kp,Fryer:1999mi,RevModPhys.74.1015,
2010ApJ...714.1217B,2010ApJ...715L.138B,Dominik:2014yma,Belczynski:2006zi,
2012ApJ...749...91F,
Wex:1998wt,1991ApJ...379L..17N,Mandel:2015spa,Abbott:2016nhf}.
A monolithic binary of black holes was recently observed by 
aLIGO~\cite{LIGOVirgo2016a}. Previously, stellar-mass black holes had only 
been seen in binaries with stellar companion (inferred from the observed spectrum
of electromagnetic waves emitted by the companion)~\cite{Lewin2010,
Remillard:2006fc,Fragos:2010tm}.
Neutron stars, on the other hand, have had numerous sightings. Thousands have
electromagnetically emitting neutron stars, or pulsars, have been documented,
in varied situations: as radio pulsars~\cite{Lattimer:2012nd,Manchester:2004bp},
in binary systems with stellar companions~\cite{1971ApJ...169L..23M,
Bond:2002eh,Lattimer:2012nd,Manchester:2004bp},
and in monolithic neutron star binaries~\cite{Hulse:1975uf,Taylor:1982wi,
Weisberg:2010zz,Lattimer:2012nd,Manchester:2004bp}.
Mixed binaries of black holes and neutron stars, is a yet undetected but 
astrophysically interesting class of systems~\cite{Wex:1998wt,
1991ApJ...379L..17N,Janka1999,Fryer:2015jpa},
which advanced GW detectors are likely to observe~\cite{Abadie:2010cfa}.

\prayush{
Coalescing binaries of compact objects, i.e. black holes (BH) and/or
neutron stars (NS) are the primary target sources for 
aLIGO~\cite{Abbott:2016nhf,LIGOVirgo2016a}.
% 
Compact binary merger rate estimates suggest
a GW detection rate of approximately a few tens of binary black holes
(BBH) every year~\cite{Abadie:2010cfa}. The actual masses of
astrophysical black holes are uncertain, but observations and
population synthesis studies suggest that BHs formed from stellar
core-collapse can have masses up to and higher than
$34M_\odot$~\cite{2008ApJ...678L..17S,2010ApJ...714.1217B}.  Also,
recent measurements using continuum fitting and X-ray reflection
fitting suggest that black holes can have high spin, with the BH
angular momentum in dimensionless units exceeding
$0.8$~\cite{2011ApJ...742...85G,2012MNRAS.424..217F,Gou:2013dna,
  2009ApJ...697..900M,McClintock:2006xd,Miller:2009cw,McClintock:2013vwa}.
}
%
